\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

First and foremost, I thank Allah for giving me the strength, patience, and clarity to complete this journey.

I would like to express my sincere gratitude to Huawei Enterprise for offering me the opportunity to carry out my final-year internship in a professional, cutting-edge environment. This experience allowed me to work on real cybersecurity and system automation challenges, and to grow both technically and personally.

I am deeply thankful to my primary mentor and company supervisor, \textbf{Arfaoui Ibrahim}, for his exceptional dedication, continuous guidance, and unwavering patience throughout this internship. From the very first day, he invested his time and energy in helping me understand the platform, refine my ideas, and overcome every obstacle. His constructive feedback, availability, and belief in my work pushed me to deliver far more than I thought possible. This project would not have reached its current form without his mentorship, and I am truly grateful for everything he taught me.

I also extend my sincere thanks to \textbf{Zhong Yan} for his valuable support, technical orientation, and insightful advice. My warmest gratitude goes to my academic supervisor, \textbf{Mongi Dziri}, for his follow-up, guidance, and academic support.

My sincere appreciation goes to the entire department, the HR team, and all my colleagues for their kindness, collaboration, and for making me feel welcome from day one. Thank you for sharing your time, knowledge, and operational experience.

Finally, I thank my family, friends, and teachers for their unconditional support during this final-year project.
