\chapter{Validation Evidence Extract}

The following table consolidates validation evidence from local project reports. These values should be kept only if they remain accurate at final submission time.

\begin{longtable}{@{}p{0.25\textwidth}p{0.25\textwidth}p{0.42\textwidth}@{}}
\caption{Validation evidence}\\
\toprule
\textbf{Artifact} & \textbf{Date} & \textbf{Evidence} \\
\midrule
\endfirsthead
\toprule
\textbf{Artifact} & \textbf{Date} & \textbf{Evidence} \\
\midrule
\endhead
\sourcefile{API_TEST_RESULTS.md} & April 15, 2026 & Core, alerts, incidents, investigations, archives, pipeline, search, dashboard, IPS, assistant, and monitoring APIs tested. \\
\sourcefile{FINAL_ACCEPTANCE_SUMMARY_17_MAI.md} & May 17, 2026 & Internal trusted mode runtime verified; backend healthy; frontend build clean; 910 core tests passed; public production readiness deferred. \\
\sourcefile{MULTI_SERVER_IMPLEMENTATION_REPORT.md} & May 28, 2026 & Multi-server gap-closing implementation completed; build and compile checks passed; limitations documented. \\
\sourcefile{MULTI_SERVER_ACTIVATION_REPORT.md} & May 28, 2026 & \codepath{multi_server_enabled=True}; dash-linux asset validated; true \codepath{asset_id} filtering confirmed. \\
\sourcefile{ADMIN_SECRET_AND_MULTI_SERVER_VERIFICATION_REPORT.md} & May 28, 2026 & Admin-secret UX implemented; assistant/operator scoping fixed; compile, TypeScript, and build checks passed. \\
\sourcefile{QA_VALIDATION_RUNTIME_INVESTIGATIONS.md} & Noted locally & Runtime investigations validated; manual workflow tests passed; full-suite limitations documented. \\
\bottomrule
\end{longtable}

\begin{table}[H]
\centering
\caption{Quantitative validation summary}
\label{tab:quant-validation}
\begin{tabularx}{\textwidth}{@{}p{0.35\textwidth}Y@{}}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Backend modules compiled & 146 \\
Automated tests passed & 910 \\
API root health check & HTTP 200 OK \\
Frontend TypeScript/build verification & Clean build \\
Multi-server asset activation & \codepath{dash-linux} validated \\
Admin-secret protected endpoints & Verified (rejection + acceptance) \\
Alerts ingested (operational data) & 2,577 \\
Incidents created & 202 \\
Investigations generated & 423 \\
\bottomrule
\end{tabularx}
\end{table}

The numbers above are derived from the local validation reports listed in Table~\ref{tab:quant-validation}. They should be updated if the final run produces different values.

